---
title: "Week 07 Assignment"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#### Exercises

```{r}
if(! require("pacman")) install.packages("pacman")

pacman::p_load(
  tidyverse,
  here,
  rvest,
  fuzzyjoin
)
```

1. Create regular expressions to find all words that:

- Start with a vowel.
- That only contain consonants. (Hint: thinking about matching “not”-vowels.)
- End with `ed`, but not with `eed.`
- End with `ing` or `ise.`

```{r}
- Start with a vowel.
^[AaEeIiOoUu]

- That only contain consonants. (Hint: thinking about matching “not”-vowels.)
[^AaEeIiOoUu]

- End with `ed`, but not with `eed.`
[^e]ed$

  
- End with `ing` or `ise.
(ing|ise)$
```


2. Create a regular expression that will match telephone numbers as commonly written in the United States.

```{r}
[0-9]{3}\-[0-9]{3}\-[0-9]{4}

```

We'll be exploring Bob Ross's paintings.

3. Load the CSV of all of his paintings.

```{r}
url <- "https://raw.githubusercontent.com/jwilber/Bob_Ross_Paintings/master/data/bob_ross_paintings.csv"

happy_trees <- 
read_csv("https://raw.githubusercontent.com/jwilber/Bob_Ross_Paintings/master/data/bob_ross_paintings.csv")

```

The following code will extract each episode and its air date from the [Joy of Painting Wikipedia page](https://en.wikipedia.org/wiki/The_Joy_of_Painting).

```{r}
jop_url <- "https://en.wikipedia.org/wiki/The_Joy_of_Painting"

webpage <- read_html(jop_url)

elements <- 
  webpage %>% 
  html_elements("li") %>% 
  html_text2() 

episode_list <- elements[str_detect(elements, "([A-Za-z]+ [0-9]{1,2}, [0-9]{4})")]
```

4. Convert `episode_list` into a dataframe such that it includes the following columns:

- `episode`: the name of the episode. Make sure to remove any extra characters (like quotes) and trim whitespace
- `air_date`: the air date of the episode as a date field
- `note`: any additional note

Name this dataframe `episode_list_df`.

```{r}
episode_list_df <-
as.data.frame(episode_list) %>%
  slice(1:403) %>%
  mutate(episode = str_extract(string = episode_list,
                               pattern = "\"(.*)\"")) %>%
  mutate(episode = str_remove_all(string = episode,
                                  pattern = "\"")) %>%
  mutate(air_date = str_extract(string = episode_list,
                                    pattern = "\\((.*)\\)")) %>%
  mutate(air_date = str_remove_all(string = air_date,
                                   pattern = "[\\(]")) %>%
  mutate(air_date = str_remove_all(string = air_date,
                                   pattern = "[\\)].*")) %>%
  mutate(air_date = as.Date(air_date, 
                           format = "%B %d, %Y"))%>%
  mutate(note = str_extract(string = episode_list,
                            pattern = "\\).*")) %>%
  mutate(note = str_remove_all(string = note,
                               pattern = "^\\)")) %>%
  mutate(note = str_remove_all(string = note,
                               pattern = "\\-")) %>%
  mutate(note = str_trim(string = note,
                         side = "both")) %>%
  select(!episode_list)
  
#So, this all worked, but it's a mess. There's got to be a better way to do this, right? I tried a bunch of different ways to try to grab just what was between the quotes or parentheses, but none of them worked. 


```

5. Join the `paintings` dataframe to the `episode_list_df` dataframe.

```{r}
happy_trees_clean <- 
  happy_trees %>%
  mutate(painting_title = str_remove_all(string = painting_title,
                                         pattern = "The\\s")) %>%
  mutate(painting_title = case_when(
    painting_title == "Mt. McKinley" ~ "Mount McKinley",
    painting_title == "Black and White Seascape" ~ "Black & White Seascape",
    painting_title == "Evening at Sunset" ~ "Evening Sunset",
    painting_title == "Misty Forest Oval" ~ "Misty Forest",
    painting_title == "Mountain Mirage Wood Shape" ~ "Mountain Mirage",
    painting_title == "Winter in Pastel" ~ "Pastel Winter",
    painting_title == "Hide A Way Cove" ~ "Hide-a-Way Cove",
    painting_title == "Golden Rays of Sunshine" ~ "Golden Rays of Sunlight",
    TRUE ~ painting_title
  ))

episode_list_clean <- 
  episode_list_df %>%
  mutate(episode = str_remove_all(string = episode,
                                         pattern = "The\\s")) %>%
  mutate(episode = case_when(
    episode == "Old Place Home" ~ "Old Home Place",
    TRUE ~ episode
  ))
  
bob_ross_joined <- 
  stringdist_full_join(
    x = episode_list_clean,
    y = happy_trees_clean,
    by = c("episode" = "painting_title")
    )



```

6. What was Bob Ross's favorite color to paint with in each season of his show? By year?

```{r}
fave_by_season <- 
bob_ross_joined %>%
  group_by(season) %>%
  summarize(across(Black_Gesso:Alizarin_Crimson, ~sum(. == TRUE))) %>%
  ungroup() %>%
  select(-season)

fave_colors_s <- 
colnames(fave_by_season)[max.col(fave_by_season, ties.method = "first")]

fave_by_year <- 
bob_ross_joined %>%  
  mutate(year = lubridate::year(air_date)) %>%
  group_by(year) %>%
  summarize(across(Black_Gesso:Alizarin_Crimson, ~sum(. == TRUE))) %>%
  ungroup() %>%
  select(-year)
  
fave_colors_y <- 
  colnames(fave_by_year)[max.col(fave_by_year, ties.method = "first")]

```

7. What words are used most frequently in the titles of his paintings? Did this change over time?

I feel like I should have been able to answer this question, because I understand the material when it is presented in class. But I appear to have a large disconnect between understanding and application, because when it comes to the homework, I can't get anything to work. I could not answer questions 6 or 7 without Googling to find the right code and even with code that worked, I couldn't put things together in the kinds of pipes we've been using. 

```{r}


# I found this and thought it was cool.

install.packages("wordcloud")
install.packages("tm")
library(wordcloud)
library(tm)

wordcloud(bob_ross_joined$painting_title, scale = c(3, .3), min.freq = 50, colors = rainbow(30))

# Here's another way to do it. And I couldn't figure anything out, so this is from stackoverflow.  

sort(table(unlist(str_split(bob_ross_joined$painting_title, 
                            pattern ="\\s"))), 
     decreasing = T)

# And here's a really dumb way to try to answer the question about changes over time because I couldn't figure that out either. 

br1983 <- 
bob_ross_joined %>%  
  mutate(year = lubridate::year(air_date)) %>%
  filter(year == "1983")

words1983 <- 
sort(table(unlist(str_split(br1983$painting_title, 
                            pattern = "\\s"))), 
     decreasing = T)

br1984 <- 
bob_ross_joined %>%  
  mutate(year = lubridate::year(air_date)) %>%
  filter(year == "1984")

words1984 <- 
sort(table(unlist(str_split(br1984$painting_title, 
                            pattern = "\\s"))), 
     decreasing = T)

br1985 <- 
bob_ross_joined %>%  
  mutate(year = lubridate::year(air_date)) %>%
  filter(year == "1985")

words1985 <- 
sort(table(unlist(str_split(br1985$painting_title, 
                            pattern = "\\s"))), 
     decreasing = T)

br1986 <- 
bob_ross_joined %>%  
  mutate(year = lubridate::year(air_date)) %>%
  filter(year == "1986")

words1986 <- 
sort(table(unlist(str_split(br1986$painting_title, 
                            pattern = "\\s"))), 
     decreasing = T)

br1987 <- 
bob_ross_joined %>%  
  mutate(year = lubridate::year(air_date)) %>%
  filter(year == "1987")

words1987 <- 
sort(table(unlist(str_split(br1987$painting_title, 
                            pattern = "\\s"))), 
     decreasing = T)

br1988 <- 
bob_ross_joined %>%  
  mutate(year = lubridate::year(air_date)) %>%
  filter(year == "1988")

words1988 <- 
sort(table(unlist(str_split(br1988$painting_title, 
                            pattern = "\\s"))), 
     decreasing = T)

br1989 <- 
bob_ross_joined %>%  
  mutate(year = lubridate::year(air_date)) %>%
  filter(year == "1989")

words1989 <- 
sort(table(unlist(str_split(br1989$painting_title, 
                            pattern = "\\s"))), 
     decreasing = T)

br1990 <- 
bob_ross_joined %>%  
  mutate(year = lubridate::year(air_date)) %>%
  filter(year == "1990")

words1990 <- 
sort(table(unlist(str_split(br1990$painting_title, 
                            pattern = "\\s"))), 
     decreasing = T)

br1991 <- 
bob_ross_joined %>%  
  mutate(year = lubridate::year(air_date)) %>%
  filter(year == "1991")

words1991 <- 
sort(table(unlist(str_split(br1991$painting_title, 
                            pattern = "\\s"))), 
     decreasing = T)

br1992 <- 
bob_ross_joined %>%  
  mutate(year = lubridate::year(air_date)) %>%
  filter(year == "1992")

words1992 <- 
sort(table(unlist(str_split(br1992$painting_title, 
                            pattern = "\\s"))), 
     decreasing = T)

br1993 <- 
bob_ross_joined %>%  
  mutate(year = lubridate::year(air_date)) %>%
  filter(year == "1993")

words1993 <- 
sort(table(unlist(str_split(br1993$painting_title, 
                            pattern = "\\s"))), 
     decreasing = T)

br1994 <- 
bob_ross_joined %>%  
  mutate(year = lubridate::year(air_date)) %>%
  filter(year == "1994")

words1994 <- 
sort(table(unlist(str_split(br1994$painting_title, 
                            pattern = "\\s"))), 
     decreasing = T)




df1983 <- 
as.data.frame(words1983)
df1984 <- 
as.data.frame(words1984)
df1985 <- 
as.data.frame(words1985)
df1986 <- 
as.data.frame(words1986)
df1987 <- 
as.data.frame(words1987)
df1988 <- 
as.data.frame(words1988)
df1989 <- 
as.data.frame(words1989)
df1990 <- 
as.data.frame(words1990)
df1991 <- 
as.data.frame(words1991)
df1992 <- 
as.data.frame(words1992)
df1993 <- 
as.data.frame(words1993)
df1994 <- 
as.data.frame(words1994)


top_ten_words_over_time <- 
as.data.frame(c(df1983[1:10,], 
                df1984[1:10,],
                df1985[1:10,],
                df1986[1:10,],
                df1987[1:10,],
                df1988[1:10,],
                df1989[1:10,],
                df1990[1:10,],
                df1991[1:10,],
                df1992[1:10,],
                df1993[1:10,],
                df1994[1:10,]
                ))
  
    
```

