---
title: "Week 06 Assignment"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This assignment is meant to reinforce our learnings from the first week of class while also providing additional background and support for using git.

We will be using GitHub for submitting assignments. We will review assignment submission during our second class. You will submit this assignment at that time.

#### Textbook


#### Exercises

```{r}
if(! require("pacman")) install.packages("pacman")

pacman::p_load(
  tidyverse,
  here,
  rvest
)
```

Create regular expressions to find all words that:

- Start with a vowel.

```{r}
"^[aeiouyAEIOUY]"
```

- That only contain consonants. (Hint: thinking about matching “not”-vowels.)

```{r}
"^[^aeiouyAEIOUY]+$"
```

- End with `ed`, but not with `eed.`

```{r}
"[^eE][eE][dD]$"
```

- End with `ing` or `ise.`

```{r}
"[ing]|[ise]$"
```


Create a regular expression that will match telephone numbers as commonly written in the United States.

```{r}
"^(\+\d{1,2}\s)?\(?\d{3}\)?[\s.-]?\d{3}[\s.-]?\d{4}$"
```


We'll be exploring Bob Ross's paintings.

Load the CSV of all of his paintings.

```{r}
url <- "https://raw.githubusercontent.com/jwilber/Bob_Ross_Paintings/master/data/bob_ross_paintings.csv"

paintings <- read_csv(url)
```

The following code will extract each episode and its air date from the [Joy of Painting Wikipedia page](https://en.wikipedia.org/wiki/The_Joy_of_Painting).

```{r}
jop_url <- "https://en.wikipedia.org/wiki/The_Joy_of_Painting"

webpage <- read_html(jop_url)

elements <- 
  webpage %>% 
  html_elements("li") %>% 
  html_text2() 

episode_list <- elements[str_detect(elements, "([A-Za-z]+ [0-9]{1,2}, [0-9]{4})")]
```

Convert `episode_list` into a dataframe such that it includes the following columns:

- `episode`: the name of the episode. Make sure to remove any extra characters (like quotes) and trim whitespace
- `air_date`: the air date of the episode as a date field
- `note`: any additional note

Name this dataframe `episode_list_df`.

```{r}
episode_list_df <-
  data.frame(episode = episode_list,
             stringsAsFactors = F) %>% 
  separate(col = episode,
           into = c("episode", "air_date", "note"),
           sep = "\\(|\\)") %>% 
  mutate(episode = str_remove_all(episode, '"'),
         episode = str_trim(episode, side = "both"),
         air_date = as.Date(air_date, format = "%B %d, %Y")) %>% 
  filter(str_detect(episode, "^[A-Za-z]"))
```

Join the `paintings` dataframe to the `episode_list_df` dataframe.

```{r}
joined_df <- 
  paintings %>% 
  left_join(episode_list_df, by = c("painting_title" = "episode"))
```


What was Bob Ross's favorite color to paint with in each season of his show? By year?

```{r}
joined_df %>%
  group_by(season) %>%
  summarise(
    across(Black_Gesso:Alizarin_Crimson, ~sum(.)) ) %>% 
  ungroup() %>% 
  pivot_longer(cols = c(-season),
               names_to = "color",
               values_to = "count") %>% 
  group_by(season) %>% 
  filter(count == max(count)) %>% 
  ungroup()
```

```{r}
joined_df %>%
  mutate(year = format(air_date, format = "%Y")) %>% 
  group_by(year) %>%
  summarise(
    across(Black_Gesso:Alizarin_Crimson, ~sum(.)) ) %>% 
  ungroup() %>% 
  pivot_longer(cols = c(-year),
               names_to = "color",
               values_to = "count") %>% 
  group_by(year) %>% 
  filter(count == max(count)) %>% 
  ungroup()
```


What words are used most frequently in the titles of his paintings? Did this change over time?

```{r}
joined_df %>% 
  select(season, painting_title) %>% 
  separate(painting_title, into = c("word1", "word2", "word3", "word4", "word5"), sep = " ") %>% 
  pivot_longer(cols = starts_with("word")) %>% 
  select(-name) %>% 
  filter(! is.na(value)) %>% 
  count(season, value) %>% 
  group_by(season) %>% 
  filter(value == max(value)) %>% 
  ungroup()
```

